%---Template Designed by Ayush Agarwal---%
\documentclass[a4paper]{article}
\usepackage[left=1.5cm,top=1cm,right=1.5cm,bottom=1cm]{geometry}
\usepackage{wrapfig}
\usepackage{array}
\usepackage{titlesec}
\pagenumbering{gobble}
\titlespacing*{\section}{0pt}{5pt}{0pt}
\author{Shikher Verma}
\begin{document}
\section*{\huge\textbf Shikher Verma}
\begin{minipage}{.45\linewidth}
	\begin{flushleft}
		3rd year, B.S. Physics, IIT Kanpur\\
		CPI: 6.3/10\\
		Github id: ShikherVerma
	\end{flushleft}
\end{minipage}
\hfill
\begin{minipage}{.45\linewidth}
	\begin{flushright}
		Phone: $(+91)9455555002$\\
		Email: $root@shikherverma.com$\\
		Website: $shikherverma.com$\\
	\end{flushright}
\end{minipage}

%----Programming Projects and Open Source Contributions---%
\section*{Programming Projects and Open Source Contributions}
\hrule
\vspace{3mm}
\begin{itemize}
	\item
	      \textbf{Online Information Management App}
	      \hfill \textit{under Prof. Manindra Agrawal, since May 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item \textbf{Lead Android Developer}, recruited and leading a team of 11 developers since May 2016.
	      	\item Working on a scalable android app, designed in MVVM using Retrofit 2 and Data Binding.
	      	\item Developed registration, login, reset password, profile, multiple channels containing items.
	      	\item Items support html/text/markdown/latex content, attachments, \# hashtag and @ mentions.
	      	\item Implemented reddit style comments. And search for channel or item using Elastic Search.
	      	\item Setup Jenkins jobs to build signed release apk and auto publish to Play Store.
	      	\item Automate building and testing of arcanist diffs and landing of accepted diffs using Jenkins.
	      \end{itemize}
	\item
	      \textbf{Autonomous Underwater Vehicle}
	      \hfill \textit{under Prof. K.S. Venkatesh \& Prof. Sachin Shinde, since Oct 2014}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item \textbf{Software Team Head}, leading a team of 5 students since August 2015.
	      	\item Built software that completes missions on an AUV. Licensed under BSD license.
	      	\item Developed simulator using Gazebo for faster testing.
	      	\item Using OpenCV for Vision and Robot Operating System (ROS) for functional design. 
	      	\item Set up Travis CI for automating building and deploying Doxygen docs to github gh-pages.
	      \end{itemize}
	\item
	      \textbf{Antaragni Festival App}
	      \hfill \textit{May 2015 - Oct 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item Built the Android application for the golden jubilee of Antaragni, cultural festival.
	      	\item Users can view schedule, event details, venue map and contact details of event organizer.
	      	\item Notifications, Result declaration, Reminders are provided through GCM.
	      	\item Licensed under Apache License. App is designed to be usable for other events.
	      \end{itemize}
	\item
	      \textbf{Startup Weekend  Techkriti}
	      \hfill \textit{March 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item Secured 3rd place; some members of the group founded a startup on the same idea.
	      	\item Developed a prototype app which helps find people to play sports with.
	      	\item After choosing a sport, users could view players on map and chat with all online players.
	      	\item Designed wireframes on planned features like location specific searching, hosting games, have game specific chat similar to mobile games and sports advertising for monetization.
	      \end{itemize}
	\item
	      \textbf{Notable Open Source contributions}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item Designed 2 customizable website \& blog templates for Jekyll. Released under MIT license.
	      	\item html-textview, added support for external image downloading libraries.
	      	\item Materialistic Hacker News, added option to reload saved page if offline data is cleared.
	      \end{itemize}
\end{itemize}

%--------Technical Skills--------%
\section*{Technical Skills}
\hrule
\vspace{3mm}
\begin{tabular}{@{}m{4.0cm}m{13cm}@{}}
	\textbf{\textrm{Languages}}        & Java (proficient), C/C++, Python, bash, HTML, CSS (basic), JavaScript (basic)      \\ 
	\textbf{\textrm{Frameworks/Tools}} & Android SDK, OpenCV, ROS, Bootstrap, Jekyll, Jenkins, Phabricator, Arcanist        \\
	\textbf{\textrm{Libraries}}        & Butterknife, DataBinding, Retrofit, Volley, rxAndroid, Stetho, Dagger, SDK Manager \\
\end{tabular}

%----Positions of Responsibility---%
\section*{Positions of Responsibility}
\hrule
\vspace{3mm}
\begin{itemize}
	\item
	      \textbf{Google Developer Group} Lead Coordinator
	      \hfill \textit{since December 2015}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item Lead Android Developer, recruited and leading a team of 11 developers since May 2016.
	      	\item Working on a scalable android app, designed in MVVM using Retrofit 2 and Data Binding.
	      	\item Developed registration, login, reset password, profile, multiple channels containing items.
	      \end{itemize}
	\item
	      \textbf{Student Guide}
	      \hfill \textit{2015-2016}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item Taught more than 15 sessions on Android, including tutorials for Software Architecture.
	      	\item Guided about 80 people through Google Study Jam and CS for Android online courses.
	      \end{itemize}
	\item
	      \textbf{Mentoring Projects}
	      \begin{itemize}
	      	\vspace{-2mm} \setlength\itemsep{-0.2em}
	      	\item Facilitated 3 students in various robotics club projects.
	      	\item Guided 6 students in programming club project.
	      	\item Member of Navya, FLOSS group. Mentored 5 students in contributing to open source.
	      \end{itemize}
\end{itemize}

%----Extracurricular activities----%
\section*{Extracurricular activities}
\hrule
\vspace{3mm}
\begin{itemize}
	\setlength\itemsep{-0.2em}
	\item Secured \textbf{1st place} in intra-college tournament Josh chess 2015. Part of college chess team 2014.
	\item All India Rating Chess Tournament 2012, secured 56th place amongst 200 participants.
	\item Secured \textbf{2nd position} in Basketball in Fresher’s Inferno in 2014, intra-college sports event.
	\item Secured \textbf{2nd position} in Lucknow Zonal BasketBall Championship 2013.
\end{itemize}

\end{document}